Dynamical modeling of tidal streams

### 2013-12-23 tex/ms.tex
streams: add pmbb figure, add to document
streams: add simulated stream figure
streams: abstract

\title{Dynamical modeling of tidal streams}
\author{Jo~Bovy\altaffilmark{1,2,3} \etal}
%  Hans-Walter~Rix\altaffilmark{4}}
\altaffiltext{\theaddress}{\label{IAS}\stepcounter{address} Institute
  for Advanced Study, Einstein Drive, Princeton, NJ 08540, USA}
\altaffiltext{\theaddress}{\label{Hubble}\stepcounter{address} Hubble
  fellow}
\altaffiltext{\theaddress}{\label{email}\stepcounter{address}
  Correspondence should be addressed to bovy@ias.edu~.}
%\altaffiltext{\theaddress}{\label{MPIA}\stepcounter{address}
%  Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117
%  Heidelberg, Germany}

\begin{abstract} 
  We present a generative, dynamical model for a tidal stream.
\end{abstract}

\keywords{
	Galaxy: fundamental parameters
	---
        Galaxy: kinematics and dynamics
        ---
	Galaxy: structure
}

@@

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lvlos.ps}
  \caption{}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
\end{figure}

@@

>>>>

\title{Dynamical modeling of tidal streams}
\author{Jo~Bovy\altaffilmark{\ref{Hubble}}}
\affil{Institute for Advanced Study, Einstein Drive, Princeton, NJ 08540, USA}
\email{bovy@ias.edu}
\altaffiltext{\theaddress}{\label{Hubble}\stepcounter{address} Hubble fellow}

\begin{abstract} 
  I present a new framework for modeling the dynamics of cold tidal
  streams that is useful for constraining the gravitational host
  potential and progenitor properties from observed tidal-stream data
  and for quickly generating mock tidal streams. The framework
  consists of simple models for the initial action--angle distribution
  of tidal debris as a function of time, which can be
  straightforwardly evolved forward in time. Taking advantage of the
  essentially one-dimensional nature of cold tidal streams, the
  transformation to position--velocity coordinates can be linearized
  and interpolated near a small number of points along the progenitor
  orbit, thus allowing for efficient computations of a stream's
  properties in observable quantities. I illustrate how to calculate
  the stream's track in different coordinate systems, how to quickly
  estimate the dispersion perpendicular to the track, and how to draw
  mock stream data. As a generative model, this framework allows one
  to compute the full probability distribution function and
  marginalize over or condition it on certain phase--space dimensions
  as well as convolve it with observational uncertainties. This will
  be instrumental in proper data analysis of stream data. In addition
  to providing a computationally-efficient practical tool for modeling
  the dynamics of tidal streams, the action--angle nature of the
  framework helps elucidate exactly in what manner streams do not
  follow single orbits, how the observed width of the stream relates
  to the velocity dispersion or mass of the progenitor, and how the
  progenitor of ``orphan'' streams could be located.

  The practical usefulness of the proposed framework crucially depends
  on the ability to calculate action--angle variables for any orbit in
  any gravitational potential. A novel method for calculating actions,
  frequencies, and angles in any static potential using a single orbit
  integration is described in an Appendix.
\end{abstract}

\keywords{
        dark matter
        ---
	Galaxy: halo
	---
        Galaxy: kinematics and dynamics
        ---
	Galaxy: structure
        ---
        galaxies: interactions
        ---
        stellar dynamics
}

@@

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \caption{}\label{fig:gd1_lbd}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}
\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lvlos.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmll.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lpmbb.ps}
  \caption{}\label{fig:gd1_lbv}
%python plot_stream.py ../tex/gd1_evol_lvlos.ps
%python plot_stream.py ../tex/gd1_evol_lpmll.ps
%python plot_stream.py ../tex/gd1_evol_lpmbb.ps
\end{figure}

@@

\begin{figure}[t!]
 \includegraphics[width=0.48\textwidth,clip=]{gd1_evol_2Gya_xz.ps}
 \includegraphics[width=0.48\textwidth,clip=]{gd1_evol_2Gya_xz_sim.ps}
  \caption{}\label{fig:gd1_sim}
%python plot_stream_2Gya.py ../tex/gd1_evol_2Gya_xz.ps
%python plot_stream_2Gya.py ../tex/gd1_evol_2Gya_xz_sim.ps
\end{figure}
